---
title: "Introduce yourself to Git"
format:
  html:
    embed-resources: true
---

## Install R package

1.  Install the `usethis` R package using the Console and command `install.packages("usethis")`.

## Git configuration

1.  Edit the code chunk below to replace the two placeholders with your own details. Ensure to keep the quotation marks.

    - `YOUR FULL NAME`: your human name, for example `"Ada Lovelace"`. This is not your GitHub username; Git uses this name to label your commits.
    - `YOUR GITHUB EMAIL`: the email address you use for your GitHub account.

```{r}
your_name <- "YOUR FULL NAME"
your_email <- "YOUR GITHUB EMAIL"
```

2.  Render the document. The next chunk checks your edits and then applies the configuration; you do not need to change it. If you have not replaced the placeholders yet, the render stops with a reminder instead of setting a broken Git identity.

```{r}
if (your_name == "YOUR FULL NAME" || your_email == "YOUR GITHUB EMAIL") {
  stop(
    "You have not added your details yet. Edit the chunk above: ",
    "replace YOUR FULL NAME with your full name and YOUR GITHUB EMAIL ",
    "with the email address you use on GitHub. Then render again.",
    call. = FALSE
  )
}

library(usethis)
use_git_config(user.name = your_name, user.email = your_email)
```

## Verify your configuration

3.  The chunk below prints a situation report of your Git setup. Good output shows your name and email in the "Git config" section and a discovered personal access token; if either is missing or wrong, repeat the step above and render again.

```{r}
usethis::git_sitrep()
```

## Next step

4.  Return to the website, you have some more work to do: <https://gitforsci-ghe.github.io/website/pre-work/06-first-repo.html#step-5-commit-and-push-your-changes>
